---
title: "IDDAP Visuals and Stats"
author: "Elnaz Ghajar-Rahimi (eg8cm)"
date: "3/23/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Loading libraries + mock sheet (pf for short)
```{r}
library(dplyr)
library(ggplot2)
library(tidyr)
library(RColorBrewer)

pf=read.csv("/Users/jessmahoney/Desktop/capstoneR/IDDAP2020/mdata.csv",stringsAsFactors=FALSE)

```

Data visualizations

Antibiotic counts
```{r}

#Bar Graph
ggplot(pf,aes(x=Antibiotic))+geom_bar(fill=brewer.pal(7,"Set1"))+ylab("Numer of Patients Taking Antibiotic")
#NOTE: the first argument in brewer.pal is the number of categories (ex the numer of antibiotic types)

#Tabulate
table(pf$Antibiotic)
```


Age, weight, and risk of readmission

Percent bar graph: antibiotic and resistant organism
```{r}
ggplot(pf,aes(x=Antibiotic,fill=Resistant.Organism..Y.N.))+geom_bar(position="fill")+labs(x="Antibiotic",y="Number of Patients")+theme(axis.text.x=element_text(angle=30),plot.title=element_text(hjust=0.5))
```

### Statistics

Average height and age of patient taking each antibiotic
```{r}
aggregate(pf[,c(3,4)], list(pf$Antibiotic),mean,na.rm=T)
```

### Extra Stuff
Making Risk of readmisison binary (Y=1, N=0)
```{r}
risk=NULL

for (i in 1:nrow(pf))
{
  if (pf[i,9]=="N") {risk[i]=0}
  else {risk[i]=1}
}


#This just adds it to a new column so that I could check if the counts were correct
revised_pf=data.frame(pf,risk)
#View(revised_pf)

#if ("High.Risk.of.Readmission"=="Y") {}
ggplot(pf,aes(x=Age,y=risk))+geom_point()
```



**Accounting for all spellings of Yes/No **

* pf_new was created to prevent overriding of original file
* Risk is the corrected version of "High Risk of Readmission"
* Resistance is the corrected version of Resistant Organism

```{r}
#Correct resistance
pf_new=pf
pf_new=pf_new%>%
mutate(Resistance=ifelse(grepl(paste(c("Y","YES","YEs","Yes","y","yE","yES","yes"),collapse="|"),Resistant.Organism..Y.N.),"Y",
ifelse(grepl(paste(c("N","NO","No","nO","no"),collapse="|"),Resistant.Organism..Y.N.),"N","Unrecognized Input"
)))

#Correct risk of readmission
pf_new=pf_new%>%
mutate(Risk=ifelse(grepl(paste(c("Y","YES","YEs","Yes","y","yE","yES","yes"),collapse="|"),High.Risk.of.Readmission),"Y",
ifelse(grepl(paste(c("N","NO","No","nO","no"),collapse="|"),High.Risk.of.Readmission),"N","Unrecognized Input"
)))


```

```{r}
#Correct gender spellings
pf_new=pf_new%>%
mutate(Sex=ifelse(grepl(paste(c("F","f"),collapse="|"),Gender..M.F.),"F",
ifelse(grepl(paste(c("M","m"),collapse="|"),Gender..M.F.),"M","Unrecognized Input"
)))

#View to check. It works!
View(pf_new)
```

