<<<<<<< HEAD
---
title: "IDDAP: Infectious Diseases Data Analysis Program"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    runtime: shiny
    social: menu
    theme: flatly
---

```{r global, include=FALSE}
library(flexdashboard)
library(ggplot2)
library(mgcv)
library(shiny)
library(dplyr)
library(readr)
library(RColorBrewer)
#newdata<-read_csv('mdata.csv')
pf=read.csv("/Users/jessmahoney/Desktop/capstoneR/IDDAP2020/mdata.csv",stringsAsFactors=FALSE)

```

Inputs {.sidebar data-width=350}
-----------------------------------------------------------------------
### File Upload {data-height=100}
```{r}
fileInput('file1', h5('Choose a file to upload'),
            accept = c('text/csv','text/comma-separated-values',
                       'text/tab-separated-values','text/plain','.csv','.tsv'))
sliderInput('age', "Age Range", min = 0, max = 110, value=c(0, 110) )
sliderInput('weight', "Weight Range (kgs) ", min = 0, max = 150, value=c(0, 150))
sliderInput('height', "Height Range (m) ", min = 0, max = 2.5, value=c(0, 2.5))
dateRangeInput('OPATad', "Admittance to the OPAT Program", start= "2005-01-01",end= "2020-01-01", min = "2005-01-01", max ="2020-01-01", startview="year")
checkboxGroupInput("resis", "Resistant Infection? (deselection will filter out the option)", choices= c("Yes"=1, "No"=2), selected = c(1,2))
checkboxGroupInput("riskofre", "High Risk of Readmission? (deselection will filter out the option)", choices= c("Yes"=1, "No"=2), selected = c(1,2))
checkboxGroupInput("MF", "Gender: (deselection will filter out the option)", choices= c("Male", "Female"), selected = c("Male", "Female"))
checkboxGroupInput("AB", "Antibiotic Type: (deselection will filter out the option)", choices= c("Erythromycin"=1, "Lymecycline"=2, "Norfloxacin"=3, "Ciprofloxacin"=4, "Amoxicillin"=5, 	"Gentamicin"=6,"Phenoxymethylpenicillin"=7, "Other"=8), selected = c(1, 2, 3, 4, 5, 6, 7, 8))

```

-----------------------------------------------------------------------
### Sorting Criteria {data-height=700}
```{r}
renderValueBox({
datafile <- eventReactive(input$file1,read.csv(input$file1$datapath))
headers = colnames(input$file1)

sliderInput('label1', headers[1], min = 0, max = 110, value=c(0, 110) )
checkboxGroupInput('check', "High Risk of Readmission? (deselection will filter out the option)", choices= c("Yes"=1, "No"=2), selected = c(1,2))
})
```

Column {data-width=250}
-----------------------------------------------------------------------
### Sorting Criteria {data-height=100}
```{r}



```
### Patient Data Output {data-height=500}

```{r}
renderTable({
  if(is.null(input$file1))
    return()
  newdata<-read_csv(input$file1$datapath)
  assign('inputfile',newdata)
  #do things to modify the "input file" below here"
  
})


```

### Data Analytics  {data-height=200}

```{r}
renderPlot({
ggplot(pf,aes(x=Antibiotic))+geom_bar(fill=brewer.pal(7,"Set1"))+ylab("Numer of Patients Taking Antibiotic")
})
```

=======
---
title: "IDDAP: Infectious Diseases Data Analysis Program"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    runtime: shiny
    social: menu
    
    theme: yeti
---

```{r global, include=FALSE}
library(flexdashboard)
library(ggplot2)
library(mgcv)
library(shiny)
library(dplyr)
library(readr)
#newdata<-read_csv('mdata.csv')

```

Inputs {.sidebar data-width=350}
-----------------------------------------------------------------------
### File Upload {data-height=100}
```{r}
fileInput('file1', h5('Choose a file to upload'),
            accept = c('text/csv','text/comma-separated-values',
                       'text/tab-separated-values','text/plain','.csv','.tsv'))

actionButton("ClearFile","Clear file")



```

-----------------------------------------------------------------------
### Sorting Criteria {data-height=700}
```{r}



```

Column {data-width=250}
-----------------------------------------------------------------------
### Sorting Criteria {data-height=100}
```{r}



```
### Patient Data Output {data-height=500}

```{r}
renderTable({
  if(is.null(input$file1))
    return()
  newdata<-read_csv(input$file1$datapath)
  assign('inputfile',newdata)
  #do things to modify the "input file" below here"
  
  
  
  
})


```

### Data Analytics  {data-height=200}

```{r}

```

>>>>>>> master
